% Exam Template using Philip Hirschhorn's exam.cls: http://www-math.mit.edu/~psh/#ExamCls
%
% run pdflatex on a finished exam at least three times to do the grading table on front page.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% These lines can probably stay unchanged, although you can remove the last two packages if you're not making pictures with tikz.
\documentclass[11pt]{exam}
\RequirePackage{amssymb, amsfonts, amsmath, latexsym, verbatim, xspace, setspace, graphicx, enumerate, paralist, array}
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}

% By default LaTeX uses large margins.  This doesn't work well on exams; problems end up in the "middle" of the page, reducing the amount of space for students to work on them.
\usepackage[margin=1in]{geometry}


% Here's where you edit the Class, Exam, Date, etc.
\newcommand{\class}{Math 2210}
\newcommand{\examnum}{Final Exam}
\newcommand{\examdate}{December 4th}
\newcommand{\timelimit}{3 Hours}


% For an exam, single spacing is most appropriate
\singlespacing
% \onehalfspacing
% \doublespacing

% For an exam, we generally want to turn off paragraph indentation
\parindent 0ex

\input{packages}

\input{custom}

\begin{document} 

% These commands set up the running header on the top of the exam pages
\pagestyle{head}
\firstpageheader{}{}{}
\runningheader{\class}{\examnum\ - Page \thepage\ of \numpages}{\examdate}
\runningheadrule

\begin{flushright}
\begin{tabular}{p{3.8in} r l}
\textbf{\class} & \textbf{Full Name:} & \makebox[2in]{\hrulefill}\\
\textbf{\term} & \textbf{ID:} & \makebox[2in]{\hrulefill}\\
\textbf{\examnum} &&\\
\textbf{\examdate} &&\\
\textbf{Time Limit: \timelimit} &
\end{tabular}\\
\end{flushright}
\rule[1ex]{\textwidth}{.1pt}

\textbf{Notes:} 
\begin{itemize}

\item On the first page, you will be asked to complete ten definitions.  Take your time, choose your words carefully, and be sure to say exactly what you mean.

\item Fully justify your responses.  Be sure to show your work clearly and logically.  Calculations that are chaotic or impossible to follow may not receive full credit, even if they are correct.

\item If you make a mistake, simply draw a line through your work to indicate that.  This way I can still read it if you change your mind!

\item Finally, don't get hung up on any one problem for too long -- you can always come back to it later!
\end{itemize}
\vsp

\addpoints

\noindent
\begin{center}
\gradetablestretch{2}
\vqword{Page}
\gradetable[v][pages]  % Use [pages] to have grading table by page instead of question
\end{center}


\newpage % End of cover page

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% See http://www-math.mit.edu/~psh/#examCls for full documentation, but the questions
% below give an idea of how to write questions [with parts] and have the points
% tracked automatically on the cover page.
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{questions}
\question[10] Give a complete definition of each of the following terms.

\begin{enumerate}[(a)]
\item a \bf relation \md on a set $A$
\vfill

\item a \bf polynomial \md over a ring $R$
\vfill

\item a \bf complex number \md
\vfill

\item a \bf subring \md of a ring $R$
\vfill

\item a \bf divisor \md of a polynomial $f(x)$ over a field $F$
\vfill
\newpage

\item an \bf irreducible \md polynomial over a field $F$
\vfill

\item a \bf primitive $n$th root of unity\md
\vfill

\item a \bf zero divisor \md in a ring $R$
\vfill

\item a \bf unit \md in a unital ring $R$
\vfill

\item a \bf monic \md polynomial over a field $F$
\vfill

\end{enumerate}
\newpage

\question[6] Identify each of the following statements as either \textbf{(T)}rue or \textbf{(F)}alse.  Whenever they are mentioned, assume that $R$ and $S$ are non-zero rings.

\noindent \textbf{Caution:} To identify a statement as true is to claim that it is \emph{guaranteed} to be true.
\vsp

\begin{enumerate}[(a)]
\item \underline{\hspace{1cm}} A binary algebraic structure can have two distinct identity elements.
\vsp

\item \underline{\hspace{1cm}} $0_{R}\cdot a = 0_{R}$ for any $a\in R$.
\vsp

\item \underline{\hspace{1cm}} The map $f:\Z\to \Z$ defined by $f(n) = 2n$ is a homomorphism.
\vsp

\item \underline{\hspace{1cm}} If $\lambda\in \C$ is a root of $f(x)\in\C[x]$, then $\CC{\lambda}$ is necessarily also a root of $f(x)$.
\vsp

\item \underline{\hspace{1cm}} The zero map $f:R\to S$ is a homomorphism.
\vsp

\item \underline{\hspace{1cm}} Every field is an integral domain.
\vsp

\item \underline{\hspace{1cm}} For any $n\in\Z^{+}$, $\ZN$ is a subring of $\Z$.
\vsp

\item \underline{\hspace{1cm}} The zero ring is a subring of $R$.
\vsp

\item \underline{\hspace{1cm}} If $\varphi:R\to S$ is an isomorphism, then $\varphi^{-1}:S\to R$ is also an isomorphism.
\vsp

\item \underline{\hspace{1cm}} If $f(x),g(x)\in R[x]$, then $\DEG{f(x)g(x)} = \DEG{f(x)}\DEG{g(x)}$.
\vsp

\item \underline{\hspace{1cm}} $\GCD{f(x),g(x)}$ is undefined if both $f(x), g(x)\in R[x]$ are the zero-polynomial.
\vsp

\item \underline{\hspace{1cm}} Every binary algebraic structure is associative, but need not be commutative.
\vsp

\item \underline{\hspace{1cm}} Every non-zero $a\in\Z_{p}$ is a unit whenever $p$ is prime.
\vsp

\item \underline{\hspace{1cm}} Every non-zero $a\in\Z_{n}$ is a zero-divisor whenever $n$ is composite.
\vsp

\item \underline{\hspace{1cm}} Every finite integral domain is a field.
\vsp

\item \underline{\hspace{1cm}} $R[x]$ is isomorphic to a subring of $R$.
\vsp


\end{enumerate}
\newpage

\question[6] Determine which of the following polynomials are irreducible.
\begin{itemize}
\item Note carefully the ring over which these polynomials are being considered.
\item Fully justify your response!
\end{itemize}
\begin{enumerate}[(a)]
\item $f(x) = x^5 + 7x + 11\in \C[x]$
\vfill

\item $g(x) = x^7 - 12x^5 + 3x^3 + 9x^2 + 213\in\Q[x]$
\vfill

\item $h(x) = 2x + 10 \in \R[x]$
\vfill

\item $w(x) = x^5 - x + 1\in \R[x]$
\vfill
\end{enumerate}
\newpage

\question[3] Show that $17x^5 + 15x^4 + 9x^3 + x^2 + 11$ is irreducible in $\Q[x]$.
\newpage

\question[3] Let $R$ and $S$ be rings and suppose $f:R\to S$ is a surjective homomorphism, and that $R$ is unital.  Prove that $f(1_{R}) = 1_{S}$.
\newpage

\question[3] Prove that $f:\Z\to \Z\times M_{2}(\R)$ defined by
\begin{center}
$f(n) = \left(n,\MATRIX{rr}{n & 0\\0 & n}\right)$ for all $n\in \Z$
\end{center}
is a homomorphism.
\newpage

\question[3] Given that $3 + i$ is a root of the polynomial
\begin{center}
$f(x) = x^4 - 8x^3 + 24x^2 - 32x + 20$,
\end{center}
find all roots of $f(x)$ in $\C$.
\newpage

\question[5] Consider the relation $T$ on $\Z$ defined by
\begin{center}
$T = \SET{(a,b)\in \Z\times \Z:a\overset{n}{\equiv} b}$.
\end{center}
That is, for any $a,b\in \Z$, then $a\sim b$ if and only if $a$ and $b$ are congruent modulo $n$.
\vsp

Prove the following statements from scratch.
\begin{enumerate}[(a)]
\item $T$ is reflexive.
\vfill

\item $T$ is symmetric.
\vfill

\item $T$ is transitive.
\vfill

\end{enumerate}
\newpage

\question[3] Solve the equation $14x = 15$ in $\Z_{17}$ by using the Euclidean algorithm to find the inverse of $14$ in $\Z_{17}$.
\vfill

\question[3] Solve the equation $52x = 26$ in $\Z_{39}$.
\vfill

\newpage

\question[5] Prove each of the following statements.
\begin{enumerate}[(a)]
\item If $x,y\in\Q$, then $x+y\in\Q$.
\vfill

\item Prove that $\sqrt{10}\notin\Q$.
\vfill

\end{enumerate}
\newpage

\question[3] Let $R$ and $S$ be rings and $f:R\to S$ be a homomorphism.  Prove that
\begin{center}
$\KER{f} = \SET{r\in R:f(r) = 0_{S}}$
\end{center}
is a subring of $R$.
\vfill

\question[2] Fill in the operation table below to define a binary operation $*$ on $S = \SET{a,b,c}$ which is commutative but not associative.
\bgroup
\begin{center}
\def\arraystretch{1.5}
\begin{tabular}{c|ccc}
* & $a$ & $b$ & $c$\\
\hline
$a$ &\\
$b$ &\\
$c$ &\\
\end{tabular}
\end{center}
\egroup

\newpage

\question[5] Let $f(x) = 2x^4 - x^3 + 4x^2 - x + 2$ and $g(x) = 2x^3 - x^2 + 2x - 1$ be considered as polynomials in $\Q[x]$.  Use the Euclidean algorithm for polynomials to calculate $\GCD{f(x),g(x)}$ and find $s(x),t(x)\in\Q[x]$ such that $\GCD{f(x),g(x)} = s(x)f(x) + t(x)g(x)$.
\newpage


\end{questions}
\end{document}