% Exam Template using Philip Hirschhorn's exam.cls: http://www-math.mit.edu/~psh/#ExamCls
%
% run pdflatex on a finished exam at least three times to do the grading table on front page.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% These lines can probably stay unchanged, although you can remove the last two packages if you're not making pictures with tikz.
\documentclass[11pt]{exam}
\RequirePackage{amssymb, amsfonts, amsmath, latexsym, verbatim, xspace, setspace, graphicx, enumerate, paralist, array}
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}

% By default LaTeX uses large margins.  This doesn't work well on exams; problems end up in the "middle" of the page, reducing the amount of space for students to work on them.
\usepackage[margin=1in]{geometry}


% Here's where you edit the Class, Exam, Date, etc.
\newcommand{\class}{Math 1070}
\newcommand{\term}{Fall 2022}
\newcommand{\examnum}{Midterm Exam 2}
\newcommand{\examdate}{November 8th}
\newcommand{\timelimit}{50 Minutes}


% For an exam, single spacing is most appropriate
\singlespacing
% \onehalfspacing
% \doublespacing

% For an exam, we generally want to turn off paragraph indentation
\parindent 0ex

\input{packages}

\input{custom}

\begin{document} 

% These commands set up the running header on the top of the exam pages
\pagestyle{head}
\firstpageheader{}{}{}
\runningheader{\class}{\examnum\ - Page \thepage\ of \numpages}{\examdate}
\runningheadrule

\begin{flushright}
\begin{tabular}{p{3.8in} r l}
\textbf{\class} & \textbf{Full Name:} & \makebox[2in]{\hrulefill}\\
\textbf{\term} & \textbf{ID:} & \makebox[2in]{\hrulefill}\\
\textbf{\examnum} &&\\
\textbf{\examdate} &&\\
\textbf{Time Limit: \timelimit} &
\end{tabular}\\
\end{flushright}
\rule[1ex]{\textwidth}{.1pt}

\textbf{Reminders:} 
\begin{itemize}

\item \textbf{Organize your work}, in a reasonably neat and coherent way, in the space provided. Work scattered all over the page without a clear ordering will 
receive very little credit.

\item \textbf{Clearly identify your final answer}, by circling it or enclosing it in a box.

\item \textbf{Unsupported answers may not receive full credit}.  A correct answer, unsupported by calculations, explanation,
or algebraic work may receive little or no credit; an incorrect answer supported by some correct calculations will likely receive partial credit.

\item \textbf{Phones should be turned off or in silent mode} -- and they should not be on your desk.  Put them away in a backpack or bag.  The same goes for smart watches.

\item \textbf{You may use a non-programmable scientific calculator.}  All you should have with you at your desk is a pencil (or pen), an eraser, and a calculator.  Beverages are fine, but nothing else should be nearby.  

\item \textbf{No scrap paper or formula sheets are allowed.}  If you need extra space, raise your hand and I will bring you extra paper.

\end{itemize}
\vsp

\addpoints

\noindent
\begin{center}
\gradetablestretch{2}
\vqword{Page}
\gradetable[v][pages]  % Use [pages] to have grading table by page instead of question
\end{center}


\newpage % End of cover page

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% See http://www-math.mit.edu/~psh/#examCls for full documentation, but the questions
% below give an idea of how to write questions [with parts] and have the points
% tracked automatically on the cover page.
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{questions}
\question[5] Solve the given system of equations, or state that it has no solutions.
\begin{center}
\systeme{y-2z=-4,x-y-3z=2,3x+2y+z=6}
\end{center}
\newpage

\fullwidth{\textbf{Please read all of the parts of this question before you start, and structure your solution accordingly.}}

\question[7] Consider the following linear programming problem.

\begin{quote}
\textbf{Minimize} the objective function
\[
C(x,y)=3x+5y
\]
subject to the constraints
\[
\begin{cases}
3x+y\geq 45\\
x+2y\geq 60\\
x,y\geq 0
\end{cases}
\]
\end{quote}
Use the space below to draw the feasible set and find all corner points of the feasible set.

\bigskip

\hfill
\begin{tikzpicture}[scale=1.2]
\begin{axis}[
	scale only axis,
	grid=both,
	grid style={line width=0.5pt, draw=gray!30},
    axis equal image,
    axis lines=middle,
    x axis line style={<->},
    y axis line style={<->},
    ticklabel style={font=\tiny},
    xtick distance=10,
    ytick distance=10,
    xmin=-15,
    xmax=85,
    ymin=-15,
    ymax=85,
    samples=50
]
\end{axis}
\end{tikzpicture}
\begin{compactenum}[(a)]
\item List \textbf{all} corner points of the feasible set.
\vspace{3cm}

\item Find the \textbf{minimum} value of $C(x,y)$ subject to the given constraints.
\end{compactenum}
\newpage

\question[5] Formulate the following as a linear programming problem. Introduce variables (with a complete sentence), and then write the objective function and the constraints.

\begin{quote}
A company advertises through Instagram and TikTok.  The cost of an ad on Instagram is \$600, and each ad on Instagram will reach 20,000 people.  The cost of an ad on TikTok is \$500, and each ad on TikTok will reach 15,000 people.
The company's weekly advertising budget is \$14,000. Since the company is targeting a younger market, at least 40\% of the total number of ads must be placed on TikTok.  How many ads should the company run on each platform per week in order to maximize the total number of people that they reach?
\end{quote}

\textbf{Remember -- you do not need to solve the problem.  But feel free to try it if you have extra time.}
\newpage

\question[6] Consider the matrix $A=\MATRIX{rr}{3 & 8\\1 & 3}$.
\begin{compactenum}[(a)]
\item Find $A^{-1}$.
\vspace{6cm}

\item Use matrix multiplication to verify that your answer to part (a) is correct.
\vspace{4cm}

\item Use your answer to part (a) to solve the linear system
\begin{center}
\systeme{3x + 8y = 7,x + 3y = 3}
\end{center}

\textbf{No points will be awarded if $A^{-1}$ is not used to solve this sytem.}
\end{compactenum}

\end{questions}
\end{document}