% Exam Template using Philip Hirschhorn's exam.cls: http://www-math.mit.edu/~psh/#ExamCls
%
% run pdflatex on a finished exam at least three times to do the grading table on front page.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% These lines can probably stay unchanged, although you can remove the last two packages if you're not making pictures with tikz.
\documentclass[11pt]{exam}
\RequirePackage{amssymb, amsfonts, amsmath, latexsym, verbatim, xspace, setspace, graphicx, enumerate, paralist, array}
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}

% By default LaTeX uses large margins.  This doesn't work well on exams; problems end up in the "middle" of the page, reducing the amount of space for students to work on them.
\usepackage[margin=1in]{geometry}


% Here's where you edit the Class, Exam, Date, etc.
\newcommand{\class}{Math 1070}
\newcommand{\term}{Winter 2023}
\newcommand{\examnum}{Midterm Exam 1}
\newcommand{\examdate}{February 10th}
\newcommand{\timelimit}{75 Minutes}


% For an exam, single spacing is most appropriate
\singlespacing
% \onehalfspacing
% \doublespacing

% For an exam, we generally want to turn off paragraph indentation
\parindent 0ex

\input{packages}

\input{custom}

\begin{document} 

% These commands set up the running header on the top of the exam pages
\pagestyle{head}
\firstpageheader{}{}{}
\runningheader{\class}{\examnum\ - Page \thepage\ of \numpages}{\examdate}
\runningheadrule

\begin{flushright}
\begin{tabular}{p{3.8in} r l}
\textbf{\class} & \textbf{Full Name:} & \makebox[2in]{\hrulefill}\\
\textbf{\term} & \textbf{ID:} & \makebox[2in]{\hrulefill}\\
\textbf{\examnum} &&\\
\textbf{\examdate} &&\\
\textbf{Time Limit: \timelimit} &
\end{tabular}\\
\end{flushright}
\rule[1ex]{\textwidth}{.1pt}

\textbf{Reminders:} 
\begin{itemize}

\item \textbf{Organize your work}, in a reasonably neat and coherent way, in the space provided. Work scattered all over the page without a clear ordering will 
receive very little credit.

\item \textbf{Clearly identify your final answer}, by circling it or enclosing it in a box.

\item \textbf{Unsupported answers may not receive full credit}.  A correct answer, unsupported by calculations, explanation,
or algebraic work may receive little or no credit; an incorrect answer supported by some correct calculations will likely receive partial credit.

\item \textbf{Phones should be turned off or in silent mode} -- and they should not be on your desk.  Put them away in a backpack or bag.  The same goes for smart watches.

\item \textbf{You may use a non-programmable scientific calculator.}  All you should have with you at your desk is a pencil (or pen), an eraser, and a calculator.  Beverages are fine, but nothing else should be nearby.  

\item \textbf{No scrap paper or formula sheets are allowed.}  If you need extra space, raise your hand and I will bring you extra paper.

\item \textbf{There is to be absolutely no talking}, whispering, or communicating in any way with anyone (except your instructor) during the test at any time.
\end{itemize}
\vsp

\addpoints

\noindent
\begin{center}
\gradetablestretch{2}
\vqword{Page}
\gradetable[v][pages]  % Use [pages] to have grading table by page instead of question
\end{center}


\newpage % End of cover page

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% See http://www-math.mit.edu/~psh/#examCls for full documentation, but the questions
% below give an idea of how to write questions [with parts] and have the points
% tracked automatically on the cover page.
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{questions}
\question[5] Let $f(x) = -x^2 + 9x - 8$.
\begin{enumerate}[(a)]
\item Is the graph of $f$ an upward facing parabola, or downward?
\vfill

\item Find the axis of symmetry.
\vfill

\item Find the vertex of $f$ (give both the $x$ and $y$-coordinate of the vertex).
\vfill

\item Find the $x$-intercepts of $f$.
\vfill

\item What is the $y$-intercept of $f$?
\vfill
\end{enumerate}
\newpage

\question[5] A small bakery determines that if their bread is priced at \$9/loaf, that they sell 65 loaves per week, but if they set the price at \$8/loaf, they sell 75 loaves per week.
\begin{enumerate}[(a)]
\item Assuming a linear relationship between supply and demand, use these observations to identify the demand equation and write the demand function in the form $p = D(q)$.
\vfill

\item At what price should the baker expect to sell 80 loaves per week?
\vfill

\item How many loaves per week should the bakery expect to sell if they set the price to \$10 per loaf?
\vfill

\item Sketch the graph of the demand equation on the axes below.  Be sure to label both axes.
\vfill

\begin{center}
\begin{tikzpicture}[scale=1]
\begin{axis}[
	grid=both,
	grid style={line width=0.5pt, draw=gray!30},
    scale only axis,
    axis lines=middle,
    x axis line style={->},
    y axis line style={->},
    ticklabel style={font=\tiny},
    xtick distance=10,
    ytick distance=2,
    ymin=0,
    ymax=16,
    xmin=0,
    xmax=100,
    samples=50
]
\end{axis}
\end{tikzpicture}
\end{center}
\end{enumerate}
\newpage

\question[5] Consider the function $g$, whose graph is pictured below.
\begin{center}
\begin{tikzpicture}[scale=1.2]
\begin{axis}[
	grid=both,
	grid style={line width=0.5pt, draw=gray!30},
	axis equal image,
    axis lines=middle,
    x axis line style={<->},
    y axis line style={<->},
    ticklabel style={font=\tiny},
	xtick distance=1,
	ytick distance=1,
    ymin=-4.5,
    ymax=4.5,
    xmin=-8.5,
    xmax=4.5,
    samples=50
]
%\node[right] at (3,2) {\footnotesize $y=g(x)$};
\addplot[domain=0:3.1,style=->]{-(x-1)^2};
%\addplot[domain=0:3.9,style=->]{-(x-1)^2+4};
%\addplot[domain=-3:0,style=-]{2*x+3};
\addplot[domain=-6:0,style=-]{-x/3 - 1};
\addplot[domain=-8:-6,style=<-]{x + 7};
%\addplot[domain=-7:-3,style=<-]{-x-6};
\end{axis}
\end{tikzpicture}
\end{center}
\begin{enumerate}[(a)]
\item For what values, if any, of $x$ is $g(x) = 0$?
\vfill

\item What is the domain of $g$?
\vfill

\item What is the range of $g$?
\vfill

\item For what values, if any, of $x$ is $g(x) = 3$?
\vfill

\item What is $g(3)$?  Don't be afraid to estimate.
\vfill

\end{enumerate}
\newpage

\question[4] Solve the linear inequality.  Express the solution using interval notation.
\begin{center}
$13x - 2(3x - 3)\geq 2x + 2(3 - 5x)$
\end{center}
\newpage

\question[4] The cost of admission to a popular music concert was \$162 for 12 children and 3 \nolinebreak adults.
The admission was \$122 for 8 children and 3 adults at the same music concert. How much was the admission for each child and adult?
 
\noindent\textbf{Note:  Be sure to clearly define your variables, and stick to your choice of notation!}
\vspace{10cm}

\question[3] Find the domain of the function $\ds{f(x) = \frac{\sqrt{x} + 1}{x - 2}}$.
\newpage

\question[4] A company's fixed weekly costs are \$700 with a variable cost of \$1 per unit.  The company can then sell those units for \$1.37 each.  
\begin{enumerate}[(a)]
\item Writing $q$ as the number of units produced and sold, find the cost, revenue, and profit functions.
\vspace{1cm}

\begin{enumerate}[(i)]
\item $C(q) =$
\vspace{1cm}

\item $R(q) =$
\vspace{1cm}

\item $P(q) =$
\vspace{1cm}
\end{enumerate}

\item How many units per week must the company sell in order to break even?
\end{enumerate}
\vspace{3cm}

\question[4] If $f(x) = 5x^2 - 1$, find $\ds{\frac{f(x +h) - f(x)}{h}}$ and simplify your answer.
\newpage

\question[3] Suppose $L$ is the line given by the equation $y = 3x + 2$.
\begin{enumerate}[(a)]
\item Find the equation of the line which is parallel to $L$ and goes through the point $(1, 1)$.
\vspace{6cm}

\item Find the equation of the line which is perpendicular to $L$ and goes through the origin $(0,0)$.
\end{enumerate} 
\end{questions}
\end{document}