% Exam Template using Philip Hirschhorn's exam.cls: http://www-math.mit.edu/~psh/#ExamCls
%
% run pdflatex on a finished exam at least three times to do the grading table on front page.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% These lines can probably stay unchanged, although you can remove the last two packages if you're not making pictures with tikz.
\documentclass[11pt, legalpaper]{exam}
\RequirePackage{amssymb, amsfonts, amsmath, latexsym, verbatim, xspace, setspace, graphicx, enumerate, paralist, array}
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}

% By default LaTeX uses large margins.  This doesn't work well on exams; problems end up in the "middle" of the page, reducing the amount of space for students to work on them.
\usepackage[margin=1in]{geometry}


% Here's where you edit the Class, Exam, Date, etc.
\newcommand{\class}{Math 1070}
\newcommand{\term}{Winter 2024}
\newcommand{\examnum}{Midterm Exam 2}
\newcommand{\examdate}{February 28th}
\newcommand{\timelimit}{75 Minutes}


% For an exam, single spacing is most appropriate
\singlespacing
% \onehalfspacing
% \doublespacing

% For an exam, we generally want to turn off paragraph indentation
\parindent 0ex

\input{packages}

\input{custom}

\begin{document} 

% These commands set up the running header on the top of the exam pages
\pagestyle{head}
\firstpageheader{}{}{}
\runningheader{\class}{\examnum\ - Page \thepage\ of \numpages}{\examdate}
\runningheadrule

\begin{flushright}
\begin{tabular}{p{3.8in} r l}
\textbf{\class} & \textbf{Full Name:} & \makebox[2in]{\hrulefill}\\
\textbf{\term} & \textbf{ID:} & \makebox[2in]{\hrulefill}\\
\textbf{\examnum} &&\\
\textbf{\examdate} &&\\
\textbf{Time Limit: \timelimit} &
\end{tabular}\\
\end{flushright}
\rule[1ex]{\textwidth}{.1pt}

\textbf{Reminders:} 
\begin{itemize}

\item \textbf{Organize your work}, in a reasonably neat and coherent way, in the space provided. Work scattered all over the page without a clear ordering will 
receive very little credit.

\item \textbf{Clearly identify your final answer}, by circling it or enclosing it in a box.

\item \textbf{Unsupported answers may not receive full credit}.  A correct answer, unsupported by calculations, explanation,
or algebraic work may receive little or no credit; an incorrect answer supported by some correct calculations will likely receive partial credit.

\item \textbf{Phones should be turned off or in silent mode} -- and they should not be on your desk.  Put them away in a backpack or bag.  The same goes for smart watches.

\item \textbf{You may use a non-programmable scientific calculator.}  All you should have with you at your desk is a pencil (or pen), an eraser, and a calculator.  Beverages are fine, but nothing else should be nearby.  

\item \textbf{No scrap paper or formula sheets are allowed.}  If you need extra space, raise your hand and I will bring you extra paper.

\item \textbf{There is to be absolutely no talking}, whispering, or communicating in any way with anyone (except your instructor) during the test at any time.
\end{itemize}
\vsp

\addpoints

\noindent
\begin{center}
\gradetablestretch{2}
\vqword{Page}
\gradetable[v][pages]  % Use [pages] to have grading table by page instead of question
\end{center}


\newpage % End of cover page

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% See http://www-math.mit.edu/~psh/#examCls for full documentation, but the questions
% below give an idea of how to write questions [with parts] and have the points
% tracked automatically on the cover page.
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{questions}
\question[4] Evaluate each of the matrix expressions if they are defined.  Otherwise, say that they are undefined.
\begin{enumerate}[(a)]
\item $\MATRIX{rrr}{1 & 5 & 2\\-1 & 0 & 1\\3 & 2 & 4} - 2\MATRIX{rrr}{6 & 1 & 3\\-1 & 1 & 2\\4 & 1 & 3}$
\vfill

\item $\MATRIX{rr}{4 & -1\\0 & 2}\MATRIX{rrr}{1 & 4 & 2\\3 & 1 & 5}$
\vfill
\end{enumerate}

\question[1] Express $\MATRIX{rrr}{5 & 6 & -7\\-1 & -2 & 3\\0 & 4 & -1}\COLUMN{u\\v\\w} = \COLUMN{2\\0\\3}$ as a linear system.

\textbf{Do not solve the system.}
\vfill

\question[2] Express \systeme{2a - 3b + 5c = 7,9a - b + c = -1,a + 5b + 4c = 0} as a matrix equation.

\textbf{Do not solve the system.}
\vfill

\newpage

\question[4] Use elementary row operations to solve the linear system \systeme{x + y - z = 7, 2x - 3y - 2z = 4,x - y - 5z = 23}

\textbf{Do not use the substitution method or elimination method.  To get credit, you must set up an augmented matrix and apply elementary row operations.}
\newpage

\question[4] Use the Inversion Algorithm to show that the matrix
\begin{center}
$A = \MATRIX{rrr}{1 & 6 & 4\\2 & 4 & -1\\-1 & 2 & 5}$
\end{center}
is not invertible.
\newpage

\question[4] For this problem it will be useful to note that that the inverse of the matrix
\begin{center}
$A = \MATRIX{rr}{4 & -1\\13 & -3}^{-1}$
\end{center} is given by
\begin{center}
$A^{-1} = \MATRIX{rr}{-3 & 1\\-13 & 4}$.
\end{center}
You do not need to justify this.  You may use this fact freely to solve the problem below.
\vsp

\noindent \textbf{Problem:} Solve the linear system
\begin{center}
\systeme{3x - y = -1,13x - 4y = 1}
\end{center}
by multiplying both sides of its corresponding matrix equation by the inverse of the coefficient matrix.
\newpage

\question[6] Suppose that the cost (in dollars) of producing $q$ units of a product is given by
\begin{center}
$C(q) = 2q + 16$
\end{center}
and the demand equation is given by
\begin{center}
$p = q - 2$
\end{center}
\begin{compactenum}[(a)]
\item Find the profit function $P(q)$.
\vspace{5cm}

\item Find the break-even point(s).
\vfill

\end{compactenum}
\newpage

\question[5] Consider the following system of linear inequalities.
\begin{center}
$\begin{cases}
3x+y > 45\\
x+2y > 60\\
x,y\geq 0
\end{cases}$
\end{center}
\vfill

Sketch its solution set on the graph below.

\hfill \begin{tikzpicture}[scale=1.2]
\begin{axis}[
	scale only axis,
	grid=both,
	grid style={line width=0.5pt, draw=gray!30},
    axis equal image,
    axis lines=middle,
    x axis line style={<->},
    y axis line style={<->},
    ticklabel style={font=\tiny},
    xtick distance=10,
    ytick distance=10,
    xmin=-15,
    xmax=85,
    ymin=-15,
    ymax=85,
    samples=50
]
\end{axis}
\end{tikzpicture}
\end{questions}
\end{document}