% Exam Template using Philip Hirschhorn's exam.cls: http://www-math.mit.edu/~psh/#ExamCls
%
% run pdflatex on a finished exam at least three times to do the grading table on front page.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% These lines can probably stay unchanged, although you can remove the last two packages if you're not making pictures with tikz.
\documentclass[11pt]{exam}
\RequirePackage{amssymb, amsfonts, amsmath, latexsym, verbatim, xspace, setspace, graphicx, enumerate, paralist, array}
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}

% By default LaTeX uses large margins.  This doesn't work well on exams; problems end up in the "middle" of the page, reducing the amount of space for students to work on them.
\usepackage[margin=1in]{geometry}


% Here's where you edit the Class, Exam, Date, etc.
\newcommand{\class}{Math 1070}
\newcommand{\term}{Fall 2022}
\newcommand{\examnum}{Midterm Exam 1}
\newcommand{\examdate}{October 7th}
\newcommand{\timelimit}{50 Minutes}


% For an exam, single spacing is most appropriate
\singlespacing
% \onehalfspacing
% \doublespacing

% For an exam, we generally want to turn off paragraph indentation
\parindent 0ex

\input{packages}

\input{custom}

\begin{document} 

% These commands set up the running header on the top of the exam pages
\pagestyle{head}
\firstpageheader{}{}{}
\runningheader{\class}{\examnum\ - Page \thepage\ of \numpages}{\examdate}
\runningheadrule

\begin{flushright}
\begin{tabular}{p{3.8in} r l}
\textbf{\class} & \textbf{Full Name:} & \makebox[2in]{\hrulefill}\\
\textbf{\term} & \textbf{ID:} & \makebox[2in]{\hrulefill}\\
\textbf{\examnum} &&\\
\textbf{\examdate} &&\\
\textbf{Time Limit: \timelimit} &
\end{tabular}\\
\end{flushright}
\rule[1ex]{\textwidth}{.1pt}

\textbf{Reminders:} 
\begin{itemize}

\item \textbf{Organize your work}, in a reasonably neat and coherent way, in the space provided. Work scattered all over the page without a clear ordering will 
receive very little credit.

\item \textbf{Clearly identify your final answer}, by circling it or enclosing it in a box.

\item \textbf{Unsupported answers may not receive full credit}.  A correct answer, unsupported by calculations, explanation,
or algebraic work may receive little or no credit; an incorrect answer supported by some correct calculations will likely receive partial credit.

\item \textbf{Phones should be turned off or in silent mode} -- and they should not be on your desk.  Put them away in a backpack or bag.  The same goes for smart watches.

\item \textbf{You may use a non-programmable scientific calculator.}  All you should have with you at your desk is a pencil (or pen), an eraser, and a calculator.  Beverages are fine, but nothing else should be nearby.  

\item \textbf{No scrap paper or formula sheets are allowed.}  If you need extra space, raise your hand and I will bring you extra paper.

\end{itemize}
\vsp

\addpoints

\noindent
\begin{center}
\gradetablestretch{2}
\vqword{Page}
\gradetable[v][pages]  % Use [pages] to have grading table by page instead of question
\end{center}


\newpage % End of cover page

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% See http://www-math.mit.edu/~psh/#examCls for full documentation, but the questions
% below give an idea of how to write questions [with parts] and have the points
% tracked automatically on the cover page.
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{questions}

\newpage
\addpoints

\question[5] A gaming company has hired a manufacturer to produce materials for first release of a new board game.  The manufacturer charges a base fee of \$7560, and an additional \$18 per copy of the game.  The company plans to sell the game for \$45 per unit.
\begin{compactenum}[(a)]
\item Find the total cost, total revenue, and total profit from producing and selling $q$ units of the game.
\vspace{1cm}

\p Total Cost: $C(q)=$
\vspace{1.5cm}

\p Total Revenue: $R(q)=$
\vspace{1.5cm}

\p Total Profit: $P(q)=$
\vspace{1.5cm}

\item How many copies of the game will the creator need to produce and sell in order to break even?
\vspace{6cm}

\item How many copies of the game will the creator need to produce and sell in order to make a profit of \$12,000?
\vspace{4cm}

\end{compactenum}
\newpage

\question[4] Consider the quadratic function $h$ whose graph is drawn below.  \textbf{You can estimate if you are not sure of the exact value of any of the following.}
\begin{multicols}{2}
\begin{center}
\begin{tikzpicture}[scale=1.1]
\begin{axis}[
	grid=both,
	grid style={line width=0.5pt, draw=gray!30},
    scale only axis,
    axis equal image,
    axis lines=middle,
    x axis line style={<->},
    y axis line style={<->},
    ticklabel style={font=\tiny},
    xtick distance=1,
    ytick distance=1,
    ymin=-5.5,
    ymax=5.5,
    xmin=-3.5,
    xmax=7.5,
    samples=50
]
\addplot[domain=-3.1:7.1,style=<->]{4-(x-2)^2/3};
%\node at (axis cs:-4,4) {\footnotesize $y=f(x)$};
\end{axis}
\end{tikzpicture}
\end{center}
\begin{compactenum}[(a)]
\item Find $h(5)$ and $h(-2)$.
\vspace{1.5cm}

\item Find all $x$ such that $h(x)=2$.
\vspace{1.5cm}

\item Find the vertex of $h$.
\vspace{1.5cm}

\item Find the $y$-intercept(s) of $h$.
\vspace{1.5cm}
\end{compactenum}
\end{multicols}

\question[3] Consider the function $\ds{g(x)=\frac{2-\sqrt{x}}{x-1}}$

\begin{compactenum}[(a)]
\item Find the domain of $g$.
\vspace{4cm}

\item Find the $x$-intercept(s) of the graph of $g$, if it has any.
\vspace{4cm}

\item Find the $y$-intercept of the graph of $g$, if it has one.

\end{compactenum}
\newpage

\question[3] Find the equation of the line that goes through the point $(2,3)$ and is perpendicular to the line with equation
\begin{center}
$\ds{y=-\frac{1}{2}x+1}$.
\end{center}
\vspace{3cm}

Graph both lines on the axes below.
\begin{center}
\begin{tikzpicture}[scale=0.9]
\begin{axis}[
	grid=both,
	grid style={line width=0.5pt, draw=gray!30},
    scale only axis,
    axis equal image,
    axis lines=middle,
    x axis line style={<->},
    y axis line style={<->},
    ticklabel style={font=\tiny},
    xtick distance=1,
    ytick distance=1,
    ymin=-5.5,
    ymax=5.5,
    xmin=-5.5,
    xmax=5.5,
    samples=50
]
%\addplot[domain=-3.1:7.1,style=<->]{4-(x-2)^2/3};
%\node at (axis cs:-4,4) {\footnotesize $y=f(x)$};
\end{axis}
\end{tikzpicture}
\end{center}

\question[4] Solve the following system of equations using any of the methods we've discussed in the course.
\begin{center}
$\systeme{3x+11y=29,-2x+3y=22}$
\end{center}
\newpage

\question[3] A manufacturer determines that the demand function for a line of bicycles is 
\begin{center}
$p=1800-3q$.
\end{center} 
where $p$ is the price (in dollars) per bicycle when $q$ bicycles are demanded per month by consumers.
\vsp

\begin{compactenum}[(a)]
\item Find the total monthly revenue $R(q)$ from producing $q$ bicycles.
\vspace{5cm}

\item How many bicycles should the manufacturer produce per month in order to maximize their revenue?
\vspace{5cm}

\item What is their maximum monthly revenue?
\end{compactenum}


\end{questions}
\end{document}