% Exam Template using Philip Hirschhorn's exam.cls: http://www-math.mit.edu/~psh/#ExamCls
%
% run pdflatex on a finished exam at least three times to do the grading table on front page.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% These lines can probably stay unchanged, although you can remove the last two packages if you're not making pictures with tikz.
\documentclass[11pt]{exam}
\RequirePackage{amssymb, amsfonts, amsmath, latexsym, verbatim, xspace, setspace, graphicx, enumerate, paralist, array}
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}

% By default LaTeX uses large margins.  This doesn't work well on exams; problems end up in the "middle" of the page, reducing the amount of space for students to work on them.
\usepackage[margin=1in]{geometry}


% Here's where you edit the Class, Exam, Date, etc.
\newcommand{\class}{Math 2210}
\newcommand{\examnum}{Midterm Exam}
\newcommand{\examdate}{October 11th}
\newcommand{\timelimit}{75 Minutes}


% For an exam, single spacing is most appropriate
\singlespacing
% \onehalfspacing
% \doublespacing

% For an exam, we generally want to turn off paragraph indentation
\parindent 0ex

\input{packages}

\input{custom}

\begin{document} 

% These commands set up the running header on the top of the exam pages
\pagestyle{head}
\firstpageheader{}{}{}
\runningheader{\class}{\examnum\ - Page \thepage\ of \numpages}{\examdate}
\runningheadrule

\begin{flushright}
\begin{tabular}{p{3.8in} r l}
\textbf{\class} & \textbf{Full Name:} & \makebox[2in]{\hrulefill}\\
\textbf{\term} & \textbf{ID:} & \makebox[2in]{\hrulefill}\\
\textbf{\examnum} &&\\
\textbf{\examdate} &&\\
\textbf{Time Limit: \timelimit} &
\end{tabular}\\
\end{flushright}
\rule[1ex]{\textwidth}{.1pt}

\textbf{Reminders:} 
\begin{itemize}

\item \textbf{Organize your work}, in a reasonably neat and coherent way, in the space provided. Work scattered all over the page without a clear ordering will 
receive very little credit.

\item \textbf{Clearly identify your final answer}, by circling it or enclosing it in a box.

\item \textbf{Unsupported answers may not receive full credit}.  A correct answer, unsupported by calculations, explanation,
or algebraic work may receive little or no credit; an incorrect answer supported by some correct calculations will likely receive partial credit.

\item \textbf{Phones should be turned off or in silent mode} -- and they should not be on your desk.  Put them away in a backpack or bag.  The same goes for smart watches.

\item \textbf{You may use a non-programmable scientific calculator.}  All you should have with you at your desk is a pencil (or pen), an eraser, and a calculator.  Beverages are fine, but nothing else should be nearby.  

\item \textbf{No scrap paper or formula sheets are allowed.}  If you need extra space, raise your hand and I will bring you extra paper.

\end{itemize}
\vsp

\addpoints

\noindent
\begin{center}
\gradetablestretch{2}
\vqword{Page}
\gradetable[v][pages]  % Use [pages] to have grading table by page instead of question
\end{center}


\newpage % End of cover page

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% See http://www-math.mit.edu/~psh/#examCls for full documentation, but the questions
% below give an idea of how to write questions [with parts] and have the points
% tracked automatically on the cover page.
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{questions}
\question[10] Complete each of the following definitions.  Abbreviations like $\exists$, $\forall$, or $\Rightarrow$ are fine, but statements are required to be complete and precise.
\begin{enumerate}[(a)]
\item Let $n\in\Z^{+}$ with $n > 1$.  An element $a\in \ZN$ is a \bf zero-divisor \md if
\vfill

\item Let $(S,*)$ be a binary algebraic structure.  An element $e\in S$ is an \bf identity \md for $*$ if
\vfill

\item Let $n\in\Z^{+}$ with $n > 1$.  An element $a\in \ZN$ is a \bf unit \md if
\vfill

\item Let $(S,*)$ and $(S',*')$ be binary algbraic structures.  An \bf isomorphism \md $\varphi:S\to S'$ is an isomorphism if
\vfill

\item $z\in\C$ is a \bf primitive root of unity \md if
\vfill

\end{enumerate}
\newpage


\question[5] The set $S = \SET{0,1,2,3}$ is a binary algebraic structure under the multiplication operation $*$ defined by
\begin{center}
$a*b = \big(\text{max}(a,b) + 1\big)\% 4$.
\end{center}
\textbf{Reminders:} For any integers $a,b\in\Z$,
\begin{itemize}
	\item $\text{max}(a,b)$ denotes the maximum of $a$ and $b$, and
	\item $a\% b$ denotes the remainder when $a$ is divided by $b$.
\end{itemize}
\begin{enumerate}[(a)]
\item Write out the multiplication table for $(S,*)$.
\vspace{8cm}

\item Show that $(S,*)$ is not associative.
\vspace{5cm}
\end{enumerate}
\newpage

\question[4] Let $n\in\Z^{+}$ with $n > 1$.  Suppose $a\in\Z$ such that $a\overset{n}{\equiv} 1$.  Prove that $\GCD{a,n} = 1$.
\vfill

\question[4] Suppose $(S,*)$ and $(S',*')$ are isomorphic binary algebraic structures.  Prove that if $(S,*)$ is associative, then so is $(S',*')$.
\vfill
\newpage

\question[4] Let $n$ be an integer which is not divisible by $5$.  Prove that the square of $n$ may be written in the form $5s+1$ or $5s + 4$ for some $s\in\Z$.
\vfill

\question[3] Find $\big(\sqrt{2} + i\sqrt{2}\big)^{10}$
\vfill

\end{questions}
\end{document}